\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-12-08 eg6-letters/NIM/EG6_RTPC_NIM.tex
more updates to the nim paper

After the ionization, the released electrons 
drift to the cylindrical detection plane under the effect of the electric field. The 
electrons released close to the cathode take the most time to reach the readout 
pads, the cylindrical symmetry insures that this maximum drift distance is the 
same for all tracks. We illustrate this in Figure~\ref{fig:RTPC_signals}, where 
we depict a typical $^{4}$He track. By measuring the maximum time ($T_{Max}$), 
we can therefore infer the drift speed of the electrons in the RTPC.\\

@@

To measure the maximum drift time, we used the time profile of hits from 
identified tracks shown in Figure~\ref{fig:TDC_profile}. We can clearly observe 
the dropping edge expected from geometrical considerations. We define a value 
$T_{Max/2}$ at which the dropping edge passes half the maximum number of hits 
in the histogram. This value was measured in bins along the 200~mm RTPC's 
length to take into account variations in the electric and magnetic field in 
the RTPC (see Figure~\ref{fig:RunNumber_61551_TDCmax_Zslice}).

\begin{figure}[tb]
\centering
\includegraphics[scale=0.42]{hits_time_profile.pdf}
\caption[]{Time distribution of the hits associated with a track in one 
experimental run. Trigger time is defined as T=15, the time unit is the ALTRO 
sampling time of 100~ns.} 
\label{fig:TDC_profile}
\end{figure}

@@

Due to the non perfect experimental conditions, in particular possible contamination 
of our gas mixture, the drift speed changed during the three months long experimental 
run\footnote{We had to increase the gas flow during the experiment due to a small leak 
in the RTPC, which concurred to the large shift of drift time observed around 
run number 61600. While our gas system was kept slightly over atmospheric 
pressure to limit contamination from air or other external gases, it is likely 
that this leak was the source of modification of the drift speed.}.  
Figure~\ref{fig:Drift_run_number_1} shows the $T_{Max/2}$ values for individual 
runs (approximately 2 hours long). We observe significant change in the drift 
speed before and after run 61600, while variations within these periods are 
around 2\%.

@@

To calibrate the gains, we compared the experimental ADCs to the energy 
deposited for each pad individually in GEANT4 by similar simulated tracks 
(using the same elastic events as for the drift paths calibration). This 
requires a very good GEANT4 simulation including drift paths and the spread of 
the charge along the path before reaching the pad, so that the simulated hits 
match the experimental ones. Moreover, the simulation has to match the DAQ 
features that can lead to cutting out some hits. After setting the simulation 
properly, we compared simulation to experiment on an event by event basis as 
shown in Figure~\ref{fig:EVENT_adc_tdc}. The gain for each pad was calculated 
as the ratio of the measured ADCs to the simulated deposited energy. Then, This 
set of the gains was applied to the experimental data. We noticed that some 
pads record lower ADCs than expected. For this reason, we wanted to make sure 
that the recorded ADCs by a given pad are similar to the ADCs recorded by other 
pads in the same track. At this step, we compared the mean ADCs of each
pad to the mean ADCs of the whole track. This ratio is collected for each pad 
from a sample of elastic events and a gain correction factor is extracted and 
applied to the first extracted gain ratio giving a final gain for each readout 
pad. Final results are shown in Figure~\ref{fig:dedx_p_exp_2nd}, where energy 
loss of particles is plotted against momentum over charge ratio. One can 
clearly see the band for $^4$He in its expected position.

>>>>

After the ionization, the released electrons drift to the cylindrical detection 
plane under the effect of the electric field. The electrons released close to 
the cathode take the most time to reach the readout pads, and the cylindrical 
symmetry ensures that this maximum drift distance is the same for all tracks.  
We illustrate this in Figure~\ref{fig:RTPC_signals}, where we depict a typical 
$^{4}$He track. Due to the non-perfect experimental conditions, in particular 
possible contamination of our gas mixture, the drift speed changed during the 
three months long experimental run\footnote{We had to increase the gas flow 
   during the experiment due to a small leak in the RTPC, which concurred to 
   the large shift of drift time observed around run number 61600. While our 
   gas system was kept slightly over atmospheric pressure to limit 
contamination from air or other external gases, it is likely that this leak was 
the source of modification of the drift speed.}. This can be calibrated by 
finding drift speed as function of experimental run-number. By measuring a 
reference time, we can therefore infer the drift speed of the electrons in the 
RTPC, by: $\textnormal{drift time} = \frac{\textnormal{drift path 
length}}{\textnormal{drift speed}}$.

@@

Figure~\ref{fig:TDC_profile} presents the time profile of hits from identified 
tracks in one z-bin along the detector in one experimental run. We can clearly 
observe the dropping edge expected from geometrical considerations. In order to 
avoid the statistical fluctuations on finding the maximum drift time 
($T_{max}$) from the time profile, we define a more stable value, i.e., 
$T_{max/2}$, at which the dropping edge passes half the maximum number of hits 
in the histogram. This value was measured in bins along the 200~mm RTPC's 
length to take into account variations in the electric and magnetic field in 
the RTPC (see Figure~\ref{fig:RunNumber_61551_TDCmax_Zslice}).

\begin{figure}[tb]
\centering
\includegraphics[scale=0.42]{hits_time_profile.pdf}
\caption[]{Time distribution of the hits in one z-bin along the RTPC in one 
experimental run. Trigger time is defined as T=15, the time unit is the ALTRO 
sampling time of 100~ns.} \label{fig:TDC_profile}
\end{figure}

@@

Figure~\ref{fig:Drift_run_number_1} shows the $T_{max/2}$ values for individual 
runs (approximately 2 hours long). We observe significant change in the drift 
speed before and after run 61600, while variations within these periods are 
around 2\%.

@@

To calibrate the gains, we compared the experimental ADCs to the energy 
deposited for each pad individually in GEANT4 by similar simulated tracks 
(using the same elastic events as for the drift paths calibration). This 
requires a very good GEANT4 simulation including drift paths and the spread of 
the charge along the path before reaching the pad, so that the simulated hits 
match the experimental ones. Moreover, the simulation has to match the DAQ 
features that can lead to cutting out some hits. After setting the simulation 
properly, we compared simulation to experiment on an event by event basis as 
shown in Figure~\ref{fig:EVENT_adc_tdc}. The gain for each pad was calculated 
as the ratio of the measured ADCs to the simulated deposited energy. Then, this 
set of the gains was applied to the experimental data. We noticed that some 
pads record lower ADCs than expected. For this reason, we wanted to make sure 
that the recorded ADCs by a given pad are similar to the ADCs recorded by other 
pads in the same track. At this step, we compared the mean ADCs of each
pad to the mean ADCs of the whole track. This ratio is collected for each pad 
from a sample of elastic events and a gain correction factor is extracted and 
applied to the first extracted gain ratio giving a final gain for each readout 
pad. Final results are shown in Figure~\ref{fig:dedx_p_exp_2nd}, where energy 
loss of particles is plotted against momentum over charge ratio. One can 
clearly see the band for $^4$He in its expected position.

### 2017-12-08 eg6-letters/NIM/review-1/review-1.tex
more updates to the nim paper

\item I don't really understand the procedure to find the drift velocity 
   described here and fig. 7. What is $Nb_{max}$ and $Nb_{max/2}$? Why does 
   $T_{max/2}$ correspond to $Nb_{max/2}$ and why is it used as $T_{max}$? If I 
   make a quick calculation and use $T_{max}$ ~ 65 * 100ns and a drift length 
   of ~ 3cm /cos(23°) ~ 7.5 cm I get a $v_{drift}$ ~ 1.15 cm/microsec << 5 
   cm/microsec which is the average value of drift velocity in drift 
   chambers.\\
The procedure according to me would be:\\
- for each hit associated to a track, whose time information is available, take 
the drift time $t_{drift_{i}}$;\\
- plot the distribution of these $t_{drift_{i}}$;\\
- find the $T_{min}$ = minimum $t_{drift_{i}}$ and $T_{max}$ = maximum 
$t_{drift_{i}}$\\
- compute $delta_{t} = T_{max} - T_{min}$ and extract the drift velocity by 
dividing the track length / $delta_{t}$. Figure 8 would have the $delta_{t}$ 
instead of the $T_{max}$ vs z.\\
Please provide more details on the applied procedure, since I have the open 
questions I wrote before and I could not understand it properly. Moreover, 
please quote the value of the found drift velocity. Is it in accordance with 
the simulations?\\
\textcolor{blue}{ }

>>>>

\item I don't really understand the procedure to find the drift velocity 
   described here and fig. 7. What is $Nb_{max}$ and $Nb_{max/2}$? Why does 
   $T_{max/2}$ correspond to $Nb_{max/2}$ and why is it used as $T_{max}$? If I 
   make a quick calculation and use $T_{max}$ ~ 65 * 100ns and a drift length 
   of ~ 3cm /cos(23$^{\circ}$) ~ 7.5 cm I get a $v_{drift}$ ~ 1.15 cm/microsec 
   << 5 cm/microsec which is the average value of drift velocity in drift 
   chambers.\\
The procedure according to me would be:\\
- for each hit associated to a track, whose time information is available, take 
the drift time $t_{drift_{i}}$;\\
- plot the distribution of these $t_{drift_{i}}$;\\
- find the $T_{min}$ = minimum $t_{drift_{i}}$ and $T_{max}$ = maximum 
$t_{drift_{i}}$\\
- compute $delta_{t} = T_{max} - T_{min}$ and extract the drift velocity by 
dividing the track length / $delta_{t}$. Figure 8 would have the $delta_{t}$ 
instead of the $T_{max}$ vs z.\\
Please provide more details on the applied procedure, since I have the open 
questions I wrote before and I could not understand it properly. Moreover, 
please quote the value of the found drift velocity. Is it in accordance with 
the simulations?\\
\textcolor{red}{- The text has been updated to clarify the procedures.\\
                - With T = 65*100~ns and drift length equal to 3cm/ 
             cos(23$^{\circ}$, $v_{drift}$ = 0.501 cm/microsec which is 
          consistent with our 0.61 cm/microsec from simulation. \\
               - In deed, we use $delta_{t} = T_{max/2} - T_{min}$ in our 
            reconstruction code.}
